plot_weight_length_cf

### 2021-12-11 smelt_2019_allseasons/f_clean_conditionfactor_survival.Rmd
Added figure of boxplots, table of survival

---
title: "Clean_Condition_Survival"
author: "Catarina Pien"
date: "12/10/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(lubridate)
library(readr)
```

@@

Summer
Yolo: 0 / 60
RV: / 60

Fall
Yolo: 
RV:
SM:
'
```{r}
(152-21)/180 #RV
(161-5)/180 #RV
(177-5-3)/180 #SM
(161-2)/180

Survivors_bycage <- CF_2019 %>%
  filter(Period == "Post",
         !Cage %in% c("FCCL1", "FCCL2")) %>%
  group_by(Deployment, Site, Cage) %>%
  summarize(n=n()) %>%
  mutate(Total = ifelse(Site == "RV", 64, 
                        ifelse(Site == "FCCL", 30, 60))) %>%
  filter(!is.na(Cage))

Survivors_bydeployment <-  Survivors_bycage %>%
  group_by(Deployment, Site) %>%
  summarize(Survived = sum(n),
            TotalFish = sum(Total)) %>%
  mutate(Prop = Survived/TotalFish) %>%
  ungroup()

Survivors_final <- Survivors_bydeployment %>% add_row(Deployment = "Summer", Site ="Yolo", Survived = 0, TotalFish = 30, Prop = 0)

@@

```{r}
Cage_survival_RV <- as.data.frame(matrix(0, ncol = 2, nrow = 384))
colnames(Cage_survival_RV) <- c("Cage", "Survived")

Cage_survival_RV$Cage <- c(rep("A", 64), rep("B", 64), rep("C", 64), rep("D", 64), rep("E", 64), rep("F", 64))
Cage_survival_RV$Survived <- c(rep("1", 60), rep("0", 4), 
                               rep("1", 64), rep("0", 0),
                               rep("1", 64), rep("0", 0),
                               rep("1", 64), rep("0", 0),
                               rep("1", 62), rep("0", 2),
                               rep("1", 56), rep("0", 8))
```

>>>>

---
title: "Clean_Condition_Survival"
author: "Catarina Pien"
date: "12/10/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---
This code takes raw summer, fall, winter data and combines it into one file of length, weight, condition factor. 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(lubridate)
library(readr)
root <- "smelt_2019_allseasons"
```

@@

Summer
Yolo: 0 / 60
RV: 152 fish on data sheet - 21 died in cage / 60 60 60

Fall
Yolo: 
RV: 161 fish on data sheet - 5 cage mortality in comments = 156/ 60 60 60
SM: 177 fish on data sheet - 5 cage mortality in comments/ 60 60 60
YB: 161 fish on data sheet - 2 "Dead in cage) = 159/ 60 60 60

Original table: https://cawater.sharepoint.com/sites/dwrdoc-aes/Shared%20Documents/Forms/AllItems.aspx?viewid=5f80dd60%2D5e8b%2D4f46%2Dab49%2D609d1052bd85&id=%2Fsites%2Fdwrdoc%2Daes%2FShared%20Documents%2FDelta%20Smelt%20Enclosure%20Study%2FPermits%2FAnnual%20Reports%2F2019%2FDelta%20Smelt%20Enclosure%20Study%202019%20Annual%20Report%20FINAL%2Epdf&parent=%2Fsites%2Fdwrdoc%2Daes%2FShared%20Documents%2FDelta%20Smelt%20Enclosure%20Study%2FPermits%2FAnnual%20Reports%2F2019

Info for this data: "V:\Data\Summer'19\August Measurements and Dissections" & "V:\Data\Summer'19\October Measurements and Dissections"
```{r}
cage <- read.csv("smelt_2019_allseasons/data_raw/Cagetype_data.csv")
# Cages B + F are large mesh
# Winter
(64+56)/(64+64) # RV 0.94

# Summer
(152-21)/180 #RV 0.73

#Fall
(161-5)/180 #RV 0.87
(177-5)/180 #SM 0.96
(161-2)/180 #YB 0.88
```

Make survival table
```{r}
Cage_survival <- as.data.frame(matrix(0, ncol = 4, nrow = 6))
colnames(Cage_survival) <- c("Deployment", "Site", "Survived", "TotalFish")
Cage_survival$Deployment = c("Winter", "Summer", "Summer", "Fall", "Fall", "Fall")
Cage_survival$Site = c("RV", "RV", "Yolo", "RV", "SM", "Yolo")
Cage_survival$Survived = c(120, 131, 0, 156, 172, 159)
Cage_survival$TotalFish = c(128, 180, 60, 180, 180, 180)

Cage_survival_total <- Cage_survival %>%
  mutate(Prop = round(Survived/TotalFish,3))

@@

```{r}
write.csv(Cage_survival_total, "smelt_2019_allseasons/data_clean/cage_survival_table.csv", row.names = FALSE)
```

### 2021-12-11 smelt_2019_allseasons/plot_weight_length_cf.Rmd
Added figure of boxplots, table of survival

---
title: "plot_weight_length_cf"
author: "Catarina Pien"
date: "12/10/2021"
output: html_document
---

@@

Plot data
```{r}
ggplot(smeltdata2, aes(x = Period, y = K, fill = Site)) + 
  geom_boxplot() + 
  facet_wrap(Deployment~.) + 
  viridis::scale_fill_viridis(discrete = TRUE, option = "plasma") + theme_bw()
```

>>>>

---
title: "plot_weight_length_cf"
author: "Catarina Pien"
date: "12/10/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

@@

Plot K
```{r}
box_K <- ggplot(smeltdata2, aes(x = Period, y = K, fill = Site)) + 
  geom_boxplot() + 
  facet_wrap(Deployment~.) + 
  viridis::scale_fill_viridis(discrete = TRUE, option = "plasma") + theme_bw()
```

Plot Length
```{r}
box_FL <- ggplot(smeltdata2, aes(x = Period, y = FL_cm, fill = Site)) + 
  geom_boxplot() + 
  facet_wrap(Deployment~.) + 
  viridis::scale_fill_viridis(discrete = TRUE, option = "plasma") + theme_bw()
```

Plot Weight
```{r}
box_Wt <- ggplot(smeltdata2, aes(x = Period, y = Weight_g, fill = Site)) + 
  geom_boxplot() + 
  facet_wrap(Deployment~.) + 
  viridis::scale_fill_viridis(discrete = TRUE, option = "plasma") + theme_bw()
```

```{r}
getwd()
library(ggpubr)
tiff(filename = file.path("smelt_2019_allseasons/figures/FL-Wt-K.tiff"), res = 300, width = 7, height = 7, units = "in", pointsize = 10, type = "cairo", compression = "lzw")
ggarrange(box_FL, box_Wt, box_K, nrow = 3)
dev.off()

```
